Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2021-06-30 main.tex
Used ieee bib settings to add et al for long references and some baselineskips to make the work fit on 12 pages Changed plot colours to match the matplotlib colours Fixed typoes throughout (response and revision) Still need to rerun simulation and update the hardware and execution parameters of new run

% Tikz reused pics
\tikzset{
   plane/.pic = {
    \draw[fill]  plot[smooth, tension=0.6] coordinates {
        (-0.65,-0.9) 
        (-0.6,-0.85) 
        (-0.4,-0.75) 
        (-0.25,-0.65) 
        (-0.15,-0.5) 
        (-0.12,-0.3) 
        (-0.1,-0.1) 
        (0,0) 
        (0.1,-0.1) 
        (0.12,-0.3) 
        (0.15,-0.5) 
        (0.25,-0.65) 
        (0.4,-0.75) 
        (0.6,-0.85) 
        (0.65,-0.9)
        } -- plot[smooth, tension=0.6] coordinates {
        (0.65,-0.9) 
        (0.15,-0.91)
        (0.35,-1.1) 
        (0.37,-1.15)
        } -- plot[smooth, tension=0.6] coordinates {
        (0.37,-1.15)
        (0,-1.12) 
        (-0.37,-1.15) 
        } -- plot[smooth, tension=0.6] coordinates {
        (-0.37,-1.15)
        (-0.35,-1.1) 
        (-0.15,-0.91) 
        (-0.65,-0.9) 
        } -- cycle;
   }
}

@@

In section \ref{sec:problem_statement}, we introduce both the cryptographic and estimation problems considered in this work, before giving some relevant preliminaries in section \ref{sec:preliminaries}. Section \ref{sec:lcao_scheme} proposes a cryptographic scheme meeting our desired security properties and section \ref{sec:priv_localization} gives a solution to the estimation problem making use of this scheme. Simulation results are discussed in section \ref{sec:sim_and_results} and concluding remarks are made in section \ref{sec:conclusion}.

@@

\subsection{Formal Cryptographic Problem} \label{subsec:crypto_problem}
The communication between the navigator and sensors in our estimation problem will be decomposed into a simple two-step bi-directional protocol that will simplify defining formal security. In section \ref{sec:priv_localization}, we will show how this protocol is sufficient to compute the location estimate at a navigator while meeting our desired privacy goals. The communication protocol is as follows.

At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, j\in\{1,\dots,m\}$ to all sensors $i\in\{1,\dots,n\}$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$. Linear combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$. This two-step linear combination aggregation protocol has been visually displayed in figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and Combination Step};
    % Navigator
    \fill (3.25,4.75) [green!80!black!60] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.9225) {plane};
    % Sensors
    \node at (1.5,1.375) {Sensor $1$};
    \fill [blue!80!black!40] (0.25,1.625) rectangle (2.875,2.625);
    \node at (1.625,2.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,1.375) {Sensor $n$};
    \fill [blue!80!black!40] (3.625,1.625) rectangle (6.25,2.625);
    \node at (5,2.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,2.125) circle (0.05);
    \fill [black] (3,2.125) circle (0.05);
    \fill [black] (3.25,2.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4.25) (5,2.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4.25) (1.5,2.875)};
    \fill [lightgray] (2.125,3.875) rectangle (4.375,3.125);
    \node at (3.25,3.5) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

    % Step 2
    \node at (3.25,0.25) {2. Aggregation Step};
    % Navigator
    \fill [green!80!black!60] (1.375,-2) rectangle (5.125,-0.25);
    \pic[xscale=0.22,yscale=0.3] at (3.25,-0.4775) {plane};
    \node at (3.25,-1.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} a_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}l^{(t)}_{i}$};
    % Sensors
    \node at (1.25,-3.875) {Sensor $1$};
    \fill  (5.25,-3.25) [blue!80!black!40] ellipse (0.4 and 0.4);
    \node at (5.25,-3.875) {Sensor $n$};
    \fill  (1.25,-3.25) [blue!80!black!40] ellipse (0.4 and 0.4);
    \fill [black] (2.75,-3.25) circle (0.05);
    \fill [black] (3.75,-3.25) circle (0.05);
    \fill [black] (3.25,-3.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(5,-2.75) (4.5,-2.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.5,-2.75) (2,-2.25)};
    \fill [lightgray] (1.625,-2.5) rectangle (2.25,-3);
    \node at (2,-2.75) {$l_1^{(t)}$};
    \fill [lightgray] (4.25,-2.5) rectangle (4.875,-3);
    \node at (4.625,-2.75) {$l_n^{(t)}$};

    % Bounding rectangles
    \draw [gray] (0,6) rectangle (6.5,1);
    \draw [gray] (0,0.75) rectangle (6.5,-4.25);
\end{tikzpicture}
\caption{Required linear combination aggregation steps at instance $t$.}
\vspace{-\baselineskip}
\label{fig:agg_steps}
\end{figure}
In addition, we note that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, j\in\{1,\dots,m\}$ to be sent from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localization}.

@@

We are now ready to define the type of encryption scheme we want for the specified communication protocol and the security guarantees it should provide. We let a linear combination aggregation scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. These will be used by a trusted setup party, the navigator and sensors $i\in\{1,\dots,n\}$. They are defined as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input of security parameter $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the navigator's public and private keys $pk_0$ and $sk_0$ and the sensor private keys $sk_i,\,i\in\{1,\dots,n\}$.
    \item[$\mathsf{Enc}(pk_0, x)$] The navigator and sensors can encrypt any value $x$ with the navigator's public key $pk_0$ and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
\end{LaTeXdescription}
The security notions we want these algorithms to meet reflect the previously stated estimation privacy goals. The navigator should learn no information from individual sensors while sensors should learn no information from the navigator or any other sensors. In the context of the introduced communication protocol, this can be summarised as the following notions.
\begin{LaTeXdescription}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,j\in\{1,\dots,m\}$ when receiving only their encryptions from the current and previous instances, and having the ability to encrypt plaintexts of their choice.
    \item[Linear Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,j\in\{1,\dots,m\}$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances. Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
\end{LaTeXdescription}
While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Ciphertext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}. Lastly, we conclude the cryptographic problem definition with the following important remark.
\begin{remark}
    A leakage function including weights from the navigator requires extra care to be taken when giving its definition. If an attacker compromises the navigator, they have control over the weights, and therefore the leakage function. We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by an attacker, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the assumption of a consistent broadcast.
\end{remark}

@@

\subsection{Joye-Libert Privacy-preserving Aggregation Scheme} \label{subsec:joye_libert_scheme}
The Joye-Libert privacy-preserving aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data and meets the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. Similarly to the Paillier scheme, it bases its security on the DCRA. A notable difference to a public-key encryption scheme is its need for a trusted party to perform the initial key generation and distribution.

@@

The function for \textit{combined} quantization and encoding, $\mathsf{E}_{M,\phi,d}(a)$, of a given number $a \in \mathbb{R}$ and with an integer range $\mathbb{Z}_M$, precision $\phi$ and scaling for $d$ prior encoded multiplications is given by
\begin{equation}
    \mathsf{E}_{M,\phi,d}(a) = \left\lfloor \phi^{d+1} a \right\rceil \pmod{M}\,. \label{eqn:encode}
\end{equation}
Decoding of an integer $u \in \mathbb{Z}_M$, is given by
\begin{equation}
    \mathsf{E}^{-1}_{M,\phi,d}(u) \!=\! 
    \begin{dcases}
        \frac{u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &u\hspace{-8pt}\pmod{M} \leq \left\lfloor\frac{M}{2}\right\rfloor \\
        -\frac{M - u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &\text{otherwise} \\
    \end{dcases}.\label{eqn:decode}
\end{equation}

@@

In general, the choice of a large precision parameter $\phi$ may reduce quantization errors introduced in \eqref{eqn:encode}, but risks overflow after too many multiplications. Given the largest number of encoded multiplications, $d_{max}$, and the largest value to be encoded $a_{max}$, the parameter should be chosen such that
\begin{equation}
    \left|\phi^{d_{max}+1}a_{max}\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
\end{equation}
In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$.

@@

As aggregation is typically performed on scalar inputs, we extend our notation for the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$. To achieve this in practice, any injective function can be used, such as the concatenation $t_{k,\tau}=k\mathbin\|\tau$. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose a the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.

@@

The security proof of this scheme must show that both encrypted weights meet IND-CPA and encrypted aggregation meets LCAO. As weights are encrypted with the Paillier encryption scheme, the first requirement is already met. To show that aggregation meets LCAO, a reduction proof is given in appendix \ref{app:proof}.

@@

\section{Privacy-Preserving Localization} \label{sec:priv_localization}
With a concrete scheme meeting the LCAO notion, we can now put forward a localisation filter with communication that can be reformulated to the required protocol. To produce an estimate of the state $\vec{x}_k$, we make use of an algebraic reformulation of the Extended Kalman Filter (EKF), the Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982}, which reduces the filter update step to a single summation. The EIF update step requires the predicted state estimate $\hat{\vec{x}}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ in the information vector and matrix forms
\begin{equation}
    \hat{\vec{y}}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\hat{\vec{x}}_{k|k-1} \quad\textrm{and}\quad \mat{Y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ sensor measurements at time $k$, with measurement models \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \begin{split}
        &\hat{\vec{y}}_{k|k} = \hat{\vec{y}}_{k|k-1} + \\
        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1})
    \end{split} \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_{k|k} = \mat{Y}_{k|k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobians
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\hat{\vec{x}}_{k|k-1}} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $i\in\{1,\dots,n\}$. After then converting the updated information vector and matrix back to state estimate $\hat{\vec{x}}_{k|k}$ and estimate covariance $\mat{P}_{k|k}$, the filter's prediction step can be computed by the navigator locally, using any suitable filter for the known system model \eqref{eqn:system_model}.

>>>>

% Tikz reused commands
\tikzset{
   plane/.pic = {
    \draw[fill]  plot[smooth, tension=0.6] coordinates {
        (-0.65,-0.9) 
        (-0.6,-0.85) 
        (-0.4,-0.75) 
        (-0.25,-0.65) 
        (-0.15,-0.5) 
        (-0.12,-0.3) 
        (-0.1,-0.1) 
        (0,0) 
        (0.1,-0.1) 
        (0.12,-0.3) 
        (0.15,-0.5) 
        (0.25,-0.65) 
        (0.4,-0.75) 
        (0.6,-0.85) 
        (0.65,-0.9)
        } -- plot[smooth, tension=0.6] coordinates {
        (0.65,-0.9) 
        (0.15,-0.91)
        (0.35,-1.1) 
        (0.37,-1.15)
        } -- plot[smooth, tension=0.6] coordinates {
        (0.37,-1.15)
        (0,-1.12) 
        (-0.37,-1.15) 
        } -- plot[smooth, tension=0.6] coordinates {
        (-0.37,-1.15)
        (-0.35,-1.1) 
        (-0.15,-0.91) 
        (-0.65,-0.9) 
        } -- cycle;
   }
}
\definecolor{pyplotblue}{RGB}{31,119,180}
\definecolor{pyplotorange}{RGB}{255,127,14}

@@

In section \ref{sec:problem_statement}, we introduce both the cryptographic and estimation problems considered in this work, before giving some relevant preliminaries in section \ref{sec:preliminaries}. Section \ref{sec:lcao_scheme} proposes a cryptographic scheme meeting our desired security properties and section \ref{sec:priv_localisation} gives a solution to the estimation problem making use of this scheme. Simulation results are discussed in section \ref{sec:sim_and_results} and concluding remarks are made in section \ref{sec:conclusion}.

@@

\subsection{Formal Cryptographic Problem} \label{subsec:crypto_problem}
The communication between the navigator and sensors in our estimation problem will be decomposed into a simple two-step bi-directional protocol that will simplify defining formal security. In section \ref{sec:priv_localisation}, we will show how this protocol is sufficient to compute the location estimate at a navigator while meeting our desired privacy goals. The communication protocol is as follows.

At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, j\in\{1,\dots,m\}$ to all sensors $i\in\{1,\dots,n\}$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$. Linear combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$. This two-step linear combination aggregation protocol has been visually displayed in figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and Combination Step};
    % Navigator
    \fill (3.25,4.75) [pyplotblue!70] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.9225) {plane};
    % Sensors
    \node at (1.5,1.375) {Sensor $1$};
    \fill [pyplotorange!70] (0.25,1.625) rectangle (2.875,2.625);
    \node at (1.625,2.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,1.375) {Sensor $n$};
    \fill [pyplotorange!70] (3.625,1.625) rectangle (6.25,2.625);
    \node at (5,2.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,2.125) circle (0.05);
    \fill [black] (3,2.125) circle (0.05);
    \fill [black] (3.25,2.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4.25) (5,2.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4.25) (1.5,2.875)};
    \fill [lightgray] (2.125,3.875) rectangle (4.375,3.125);
    \node at (3.25,3.5) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

    % Step 2
    \node at (3.25,0.25) {2. Aggregation Step};
    % Navigator
    \fill [pyplotblue!70] (1.375,-2) rectangle (5.125,-0.25);
    \pic[xscale=0.22,yscale=0.3] at (3.25,-0.4775) {plane};
    \node at (3.25,-1.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} a_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}l^{(t)}_{i}$};
    % Sensors
    \node at (1.25,-3.875) {Sensor $1$};
    \fill  (5.25,-3.25) [pyplotorange!70] ellipse (0.4 and 0.4);
    \node at (5.25,-3.875) {Sensor $n$};
    \fill  (1.25,-3.25) [pyplotorange!70] ellipse (0.4 and 0.4);
    \fill [black] (2.75,-3.25) circle (0.05);
    \fill [black] (3.75,-3.25) circle (0.05);
    \fill [black] (3.25,-3.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(5,-2.75) (4.5,-2.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.5,-2.75) (2,-2.25)};
    \fill [lightgray] (1.625,-2.5) rectangle (2.25,-3);
    \node at (2,-2.75) {$l_1^{(t)}$};
    \fill [lightgray] (4.25,-2.5) rectangle (4.875,-3);
    \node at (4.625,-2.75) {$l_n^{(t)}$};

    % Bounding rectangles
    \draw [gray] (0,6) rectangle (6.5,1);
    \draw [gray] (0,0.75) rectangle (6.5,-4.25);
\end{tikzpicture}
\caption{Required linear combination aggregation steps at instance $t$.}
\label{fig:agg_steps}
\end{figure}
In addition, we note that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, j\in\{1,\dots,m\}$ to be sent from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localisation}.

@@

We are now ready to define the type of encryption scheme we want for the specified communication protocol and the security guarantees it should provide. We let a linear combination aggregation scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. These will be used by a trusted setup party, the navigator and sensors $i\in\{1,\dots,n\}$. They are defined as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input of security parameter $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the navigator's public and private keys $pk_0$ and $sk_0$ and the sensor private keys $sk_i,\,i\in\{1,\dots,n\}$.
    \item[$\mathsf{Enc}(pk_0, x)$] The navigator and sensors can encrypt any value $x$ with the navigator's public key $pk_0$ and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
\end{LaTeXdescription}
The security notions we want these algorithms to meet reflect the previously stated estimation privacy goals. The navigator should learn no information from individual sensors while sensors should learn no information from the navigator or any other sensors. In the context of the introduced communication protocol, this can be summarised as the following notions.
\begin{LaTeXdescription}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,j\in\{1,\dots,m\}$ when receiving only their encryptions from the current and previous instances and having the ability to encrypt plaintexts of their choice.
    \item[Linear Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,j\in\{1,\dots,m\}$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances. Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
\end{LaTeXdescription}
While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Plaintext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}. Lastly, we conclude the cryptographic problem definition with the following important remark.
\begin{remark}
    A leakage function including weights from the navigator requires extra care to be taken when giving its definition. If an attacker compromises the navigator, they have control over the weights, and therefore the leakage function. We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by an attacker, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the assumption of a consistent broadcast.
\end{remark}

@@

\subsection{Joye-Libert Privacy-Preserving Aggregation Scheme} \label{subsec:joye_libert_scheme}
The Joye-Libert privacy-preserving aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data and meets the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. Similarly to the Paillier scheme, it bases its security on the DCRA. A notable difference to a public-key encryption scheme is its need for a trusted party to perform the initial key generation and distribution.

@@

The function for \textit{combined} quantisation and encoding, $\mathsf{E}_{M,\phi,d}(a)$, of a given number $a \in \mathbb{R}$ and with an integer range $\mathbb{Z}_M$, precision $\phi$ and scaling for $d$ prior encoded multiplications is given by
\begin{equation}
    \mathsf{E}_{M,\phi,d}(a) = \left\lfloor \phi^{d+1} a \right\rceil \pmod{M}\,. \label{eqn:encode}
\end{equation}
Decoding of an integer $u \in \mathbb{Z}_M$, is given by
\begin{equation}
    \mathsf{E}^{-1}_{M,\phi,d}(u) \!=\! 
    \begin{dcases}
        \frac{u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &u\hspace{-8pt}\pmod{M} \leq \left\lfloor\frac{M}{2}\right\rfloor \\
        -\frac{M - u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &\text{otherwise} \\
    \end{dcases}.\label{eqn:decode}
\end{equation}

@@

In general, the choice of a large precision parameter $\phi$ may reduce quantisation errors introduced in \eqref{eqn:encode}, but risks overflow after too many multiplications. Given the largest number of encoded multiplications, $d_{max}$, and the largest value to be encoded $a_{max}$, the parameter should be chosen such that
\begin{equation}
    \left|\phi^{d_{max}+1}a_{max}\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
\end{equation}
In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$.

@@

As aggregation is typically performed on scalar inputs, we extend our notation to the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$. To achieve this in practice, any injective function can be used, such as the concatenation $t_{k,\tau}=k\mathbin\|\tau$. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose a the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.

@@

The security proof of this scheme must both show that encrypted weights meet IND-CPA and that encrypted aggregation meets LCAO. As weights are encrypted with the Paillier encryption scheme, the first requirement is already met. To show that aggregation meets LCAO, a reduction proof is given in appendix \ref{app:proof}.

@@

\section{Privacy-Preserving Localisation} \label{sec:priv_localisation}
With a concrete scheme meeting the LCAO notion, we can now put forward a localisation filter with communication that can be reformulated to the required protocol. To produce an estimate of the state $\vec{x}_k$, we make use of an algebraic reformulation of the Extended Kalman Filter (EKF), the Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982}, which reduces the filter update step to a single summation. The EIF update step requires the predicted state estimate $\hat{\vec{x}}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ in the information vector and matrix forms
\begin{equation}
    \hat{\vec{y}}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\hat{\vec{x}}_{k|k-1} \quad\textrm{and}\quad \mat{Y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ sensor measurements at time $k$, with measurement models \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \begin{split}
        &\hat{\vec{y}}_{k|k} = \hat{\vec{y}}_{k|k-1} + \\
        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1})
    \end{split} \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_{k|k} = \mat{Y}_{k|k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobians
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\hat{\vec{x}}_{k|k-1}} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $i\in\{1,\dots,n\}$. After then converting the updated information vector and matrix back to state estimate $\hat{\vec{x}}_{k|k}$ and estimate covariance $\mat{P}_{k|k}$, the filter's prediction step can be computed by the navigator locally, using any suitable filter for the known system model \eqref{eqn:system_model}.

In the form above, at every timestep $k$, all sensitive sensor information required for state estimation is captured in the measurement vector
\begin{equation}
    \vec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1}) \label{eqn:measurement_vec}
\end{equation}
and the measurement matrix
\begin{equation}
    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
\end{equation}
namely, their measurements $z_{k,i}$, measurement variances $r_{k,i}$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$. However, $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ also require the current predicted state estimate $\hat{\vec{x}}_{k|k-1}$ to be computed (in $h_i$ and $\mat{H}_{k,i}$). For this reason, our goal is to reformulate \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} to be computable at each sensor $i$ as a linear combination of functions of the navigator state estimate (the navigator weights), to be subsequently aggregated at the navigator. Application of the linear combination aggregation scheme proposed would in turn guarantee that sensors do not learn the navigator state, and the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
